Testing Methodologies for Asynchronous Centralized Simulations\\

### 2020-12-05 paper/PaperDraft2.tex
Minor fix
Minor Paper Changes
CHanged the order of a figure
My Final paper update

\subsection{AutomatedFull-stack Testing}

@@

After all of the ticks have been ran, we may leverage a debugging interface opened in the server(Listing 6, line 6), which returns the internal snapshot of the simulation from the server. 
Using this snapshot, we will verify that the server copy of each tank's score, location and chat messages matches the authoritative snapshot. Putting it all together, we arrive at Fig. 14, which 
has all of the client instances performing the random actions and a representation of the test results. In this case, the framework has detected a discrepancy of Player 2's position on his own
instance.

@@

>>>>

@@

After all of the ticks have been ran, we may leverage a debugging interface opened in the server(Listing 6, line 6), which returns the internal snapshot of the simulation from the server. 
Using this snapshot, we will verify that the server copy of each tank's score, location and chat messages matches the authoritative snapshot. Putting it all together, we arrive at Fig. 14, which 
has all of the client instances performing the random actions and a representation of the test results. In this case, the framework has detected a discrepancy of Player 2's position on his own
instance. The reader is encouraged to download and run these test cases in order to see the dynamic control in action.

@@

In conclusion, we have proposed and implemented several testing techniques for asynchronous certralized simulations. We have provided a generalized set of architectures which we then proceeded to 
implement in NodeTank. In doing so, we have learned how to deal with asynchronous workflows and the tools necessary to implement new features into implementations of this type. In doing so, we not only providedthe reader with 
the requied knowledge to deal with testing centralized simulations, but the authors have also increased their knowledge base with the goal of continuing such research in the future.
